A Survey on Ordered Binary Decision Diagrams

### 2015-09-12 paper.tex
Add ITE operator to Implementational aspects intro
Add ITE operator subsection
Remove ITE emphasis
Finish hash-based caches

Hence, the following sections cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. efficient data structures, how
to possibly approach the variable ordering problem and \textit{garbage collection}.
\tbr

@@

There exists a special version of hash tables, so-called
\textit{hash-based caches}, which do not resolve collisions, i.e. overwrite
existing entries. \textit{Hash-based caches} issue a cache miss if a looked up
element is not found. \tbr

>>>>

Hence, the following sections cover important aspects to keep in mind when
implementing an OBDD framework efficiently, i.e. efficient data structures, the
ITE operator, how to possibly approach the variable ordering problem and
\textit{garbage collection}. \tbr

@@

There exists a special version of hash tables, so-called
\textit{hash-based caches}, which do not resolve collisions, i.e. overwrite
existing entries, and issue a cache miss if a looked up element is not found.
As will be seen, \textit{Hash-based caches} are useful to provide an efficient
implementation of the ITE operator. \tbr

\subsection{ITE Operator}
\label{subsec:ite-operator}
